\documentclass[10pt,a4paper]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[margin=1.45cm]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{fontawesome5}
\usepackage{microtype}
\usepackage{xcolor}
\usepackage{multicol}

\setlength{\parindent}{0pt}
\setlength{\columnsep}{0.8cm}
\setlength{\columnseprule}{0.4pt}
\setlength{\multicolsep}{4pt}

% Section styling
\titleformat{\section}{\normalsize\bfseries}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{0.45em}{0.25em}

% Compact lists
\setlist[itemize]{leftmargin=1.2em, itemsep=1pt, topsep=2pt, parsep=0pt, partopsep=0pt}

\hypersetup{
  colorlinks=true,
  linkcolor=black,
  urlcolor=blue
}
\urlstyle{same}

\begin{document}
\pagestyle{empty}

\begin{center}
  {\Large \textbf{Solon Falas}}\\[2pt]
  \footnotesize
  \faEnvelope\ \href{mailto:falas.solon@ucy.ac.cy}{falas.solon@ucy.ac.cy}
  \quad|\quad
  \faLinkedin\ \href{https://www.linkedin.com/in/solon-falas/}{linkedin.com}
  \quad|\quad
  \faGraduationCap\ \href{https://scholar.google.com/citations?user=C1OPsJIAAAAJ}{Google Scholar}
  \quad|\quad
  \faOrcid\ \href{https://orcid.org/0000-0003-1182-4382}{ORCiD}
\end{center}

\vspace{0.2em}
\small

\begin{multicols}{2}

\section*{Professional Summary}
Machine learning engineer and data scientist with 7+ years of hands-on experience building, training, and evaluating ML models for real-world applications. Proven track record designing physics-informed neural networks, running end-to-end model development workflows — data preprocessing, feature engineering, hyperparameter optimization, and benchmarking — and delivering results through peer-reviewed publications. Comfortable across the full ML stack, from raw data and simulation outputs to reproducible, production-quality pipelines, using Python, TensorFlow, PyTorch, and standard data science tooling.

\section*{Professional Strengths}
\begin{itemize}
    \item End-to-end ML model development, evaluation, and benchmarking
    \item Data preprocessing, feature engineering, and pipeline design
    \item Hyperparameter optimization and systematic experimentation
    \item Statistical analysis and data-driven decision making
    \item Clear technical communication for mixed audiences
    \item Strong documentation and reproducibility practices
\end{itemize}

\section*{Technical Skills}
\textbf{Programming:} Python, C/C++/C\#, \LaTeX\\[2pt]
\textbf{ML / Data:} TensorFlow, PyTorch, Optuna, Data Analytics\\[2pt]
\textbf{Tools:} Linux, Git, MATLAB, PowerWorld\\[2pt]
\textbf{Domains:} ML model development, power systems, embedded systems, IoT security

\section*{Education}
\textbf{Ph.D., Computer Engineering} (2017--2025)\\
University of Cyprus, Nicosia, Cyprus\\
\textit{Cross-Layer Physics-based Security for Cyber-Physical Systems}\\[4pt]

\textbf{B.Sc., Computer Engineering} (2013--2017)\\
University of Cyprus, Nicosia, Cyprus

\section*{Awards}
\begin{itemize}
  \item \textbf{Best Computer Engineering Undergraduate Dissertation}, University of Cyprus (2017)
  \item \textbf{Ph.D. Scholarship}, KIOS Research and Innovation Center of Excellence (2017--2025)
\end{itemize}

\section*{Hobbies \& Activities}
\begin{itemize}
  \item Personal finance, portfolio construction and management, risk analysis, investing
  \item Running, weightlifting, fitness, sports
  \item Digital privacy enthusiast, DIY self-hosting services and smart-home projects
\end{itemize}

\section*{Languages}
Greek (Native)\\
English (Fluent)

\section*{Professional Experience}
\textbf{Research Associate -- Applied ML \& Embedded Security} (2025--Present)\\
KIOS Research and Innovation Center of Excellence, University of Cyprus
\begin{itemize}
  \item Contributing to applied research and engineering activities in machine learning, cyber-physical systems, and embedded security.
\end{itemize}

\textbf{Researcher -- ML Engineering \& Data Science} (2017--2025)\\
KIOS Research and Innovation Center of Excellence, University of Cyprus
\begin{itemize}
  \item Designed and trained physics-informed neural networks (PINNs) for power-system state estimation, embedding domain constraints as physics-based regularization to improve model generalization.
  \item Built end-to-end Python data pipelines to ingest, preprocess, and curate multi-scenario power-system simulation datasets for model training and validation.
  \item Ran systematic hyperparameter optimization with Optuna and evaluated models across noisy, faulted, and adversarially manipulated datasets, analyzing estimation-error metrics and robustness across diverse operating conditions.
  \item Designed a modular secure firmware-update framework for embedded devices, combining hardware-based authentication with device-specific delivery to eliminate long-term secret storage.
  \item Maintained reproducible experimental workflows with version-controlled code, documented configurations, and benchmarking reports using Python, TensorFlow, PyTorch, and MATLAB.
\end{itemize}

\textbf{Teaching Assistant -- Computer Engineering} (2017--2025)\\
University of Cyprus
\begin{itemize}
  \item Supported lab-based courses including digital logic, microprocessors, operating systems, and VLSI CAD.
  \item Provided hands-on technical guidance, prepared lab material, and assisted with grading and examination support.
\end{itemize}

\section*{Selected Technical Work}
\textbf{Robust State Estimation for Power Systems}
\begin{itemize}
  \item Applied physics-informed ML to improve estimation reliability in the presence of bad data, faults, and adversarial inputs.
\end{itemize}

\textbf{Secure Firmware Updates for Embedded Devices}
\begin{itemize}
  \item Designed an end-to-end architecture for authenticated firmware delivery with hardware-assisted device binding and reduced secret-storage requirements.
\end{itemize}

\section*{Selected Publications}
\footnotesize
\begin{itemize}
  \item S. Falas, M. Asprou, C. Konstantinou, and M. K. Michael, ``Robust Power System State Estimation Using Physics-Informed Neural Networks,'' \textit{IEEE Transactions on Industrial Informatics}, 2025.
  \item S. Falas, M. Asprou, C. Konstantinou, and M. K. Michael, ``Data Manipulation Attack Mitigation in Power Systems Using Physics-Informed Neural Networks,'' \textit{IEEE CSR}, 2025.
  \item S. Falas, M. Asprou, C. Konstantinou, and M. K. Michael, ``Physics-Informed Neural Networks for Accelerating Power System State Estimation,'' \textit{ISGT Europe}, 2023.
  \item S. Falas, C. Konstantinou, and M. K. Michael, ``A Modular End-to-End Framework for Secure Firmware Updates on Embedded Systems,'' \textit{ACM Journal on Emerging Technologies in Computing Systems (JETC)}, 2022.
  \item S. Falas, C. Konstantinou, and M. K. Michael, ``Physics-Informed Neural Networks for Securing Water Distribution Systems,'' \textit{IEEE ICCD}, 2020.
  \item S. Falas, C. Konstantinou, and M. K. Michael, ``Hardware-Enabled Secure Firmware Updates in Embedded Systems,'' \textit{VLSI-SoC}, 2019.
\end{itemize}
\normalsize

\end{multicols}

\end{document}